{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2025-11-17 notes.tex
Fixes for fifth lecture
Fixes for lecture 30.10.25
Some exercise answers

% Packages
\usepackage{subfiles}    % Allows compiling chapters as standalone documents
\usepackage{slashed}    % Dirac slash notation
\usepackage{amsmath}  % For pmatrix, boldsymbol and eqref
\usepackage{amssymb}  % For fractur
\usepackage{textcomp} 
\usepackage[utf8]{inputenc}  % Taken out when using LuLaTeX
%\usepackage{unicode-math}  % Would like to use this in particular to get blackboard bold numbers, but collides with greek letters in headers
\usepackage[bb=dsserif]{mathalpha} % Makes blackboard bold numbers work
\usepackage{a4wide}
\usepackage{caption}
\usepackage{color, enumerate, graphicx}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage[answerdelayed]{exercise} % Package for exercises, set to delay answers to end

@@

% Make exercise headers a bit better
\renewcounter{Exercise}[chapter]
\renewcommand{\ExerciseHeader}{\centerline{\textbf{\large
\ExerciseName\,\thechapter.\ExerciseHeaderNB\ExerciseHeaderTitle
\ExerciseHeaderOrigin\medskip}}}
\renewcommand{\AnswerHeader}{\medskip\noindent\textbf{
\ExerciseName\ \thechapter.\ExerciseHeaderNB}\newline\smallskip}

@@

The notes are based on lectures given at the University of Oslo in 2011, 2013, 2015, 2017, 2019, 2021, 2023, and 2025, and lectures at the NORDITA Winter School on Theoretical Particle Physics in 2012.  Several student have contributed significantly to the notes. We owe a particular gratitude to Paul Batzing, who took notes during the first version of the lectures in 2011, forming the start of this document, and to Carl Martin Favang who has fixed many of my mistakes. Morten Tryti Berg has supplied a solution to one of the exercises.

>>>>

% Packages
\usepackage{subfiles}    % Allows compiling chapters as standalone documents
\usepackage{slashed}    % Dirac slash notation
\usepackage{amsmath}  % For pmatrix, boldsymbol and eqref
\usepackage{amssymb}  % For fractur
\usepackage{textcomp} 
\usepackage[utf8]{inputenc}  % Taken out when using LuLaTeX
%\usepackage{unicode-math}  % Would like to use this in particular to get blackboard bold numbers, but collides with greek letters in headers
%\usepackage[bb=dsserif]{mathalpha} % Makes blackboard bold numbers work
\usepackage[bb=dsserif]{mathalfa} % Called mathalfa in some older TeX distributions 
\usepackage{a4wide}
\usepackage{caption}
\usepackage{color, enumerate, graphicx}
\usepackage{hyperref}
%\usepackage[normalem]{ulem} % What is this used for?
\usepackage[answerdelayed]{exercise} % Package for exercises, set to delay answers to end

@@

% Make exercise headers a bit better
\renewcounter{Exercise}[chapter]
% Header for exercise
\renewcommand{\ExerciseHeader}{\noindent\textbf{\ExerciseName\,\thechapter.\ExerciseHeaderNB\,\ExerciseHeaderDifficulty\,\ExerciseHeaderTitle\ExerciseHeaderOrigin\newline}}
\renewcommand{\AtBeginExercise}{\noindent\hspace{-2.1mm}}
% Header for answer
\renewcommand{\AnswerHeader}{\noindent\textbf{\ExerciseName\ \thechapter.\ExerciseHeaderNB}\newline}

@@

The notes are based on lectures given at the University of Oslo in 2011, 2013, 2015, 2017, 2019, 2021, 2023, and 2025, and lectures at the NORDITA Winter School on Theoretical Particle Physics in 2012.  Several student have contributed significantly to the notes. We owe a particular gratitude to Paul Batzing, who took notes during the first version of the lectures in 2011, forming the start of this document, and to Carl Martin Favang who has fixed many of my mistakes. Carl Fredrik Andresen, Morten Tryti Berg and Brage Andreas Trefjord have supplied solutions to one or more exercises.
